Towards Transparency and Open Science

### 2023-01-06 manuscript.Rmd
typo

<!--the appraisal of "induced theories" should be low-->
So what to think of such, yet untested, theory?
Researchers and philosophers of science differ considerably their opinion about to appraise theories, e.g., judging the long-term performance (if they are frequentists), degrees of belief (if they are Bayesians), or probativeness [if they are severe testers, @mayoStatisticalInferenceSevere2018, p. 14] of a hypothesis.
Whatever measure they subscribe to, an untested theory should not score very high on it.

>>>>

<!--the appraisal of "induced theories" should be low-->
So what to think of such, yet untested, theory?
Researchers and philosophers of science differ considerably in their opinion about how to appraise theories, e.g., judging the long-term performance (if they are frequentists), degrees of belief (if they are Bayesians), or probativeness [if they are severe testers, @mayoStatisticalInferenceSevere2018, p. 14] of a hypothesis.
Whatever measure they subscribe to, an untested theory should not score very high.
